---
title: "Filene IRT models"
author: "Rachael Pyram"
date: "2023-09-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Reading in data  
```{r}
dat = read.csv('dicho-data.csv')

```


# The Leslie et al. model  
This model proposes three strategies: 
+ The **resource** strategy includes preferential treatment, targeted recruitment, diversity statements, targeted training, diversity networking groups, and diversity mentoring programs  
+ The **accountability** strategy includes diversity plans, diversity performance evals, diversity positions, and grievance systems  
+ The **nondiscrimination** strategy includes merit-based decision making and general diversity training  

```{r}
##note: numbers refer to cols in the df; see sheet 'ColNumKey in 'irt-output.xlsx' for variable names + description
  
#F1 = resource strategy, F2 = accountability strategy, F3 = nondiscrimination strategy
leslie = 'F1 = 1-2, 23-27, 33-36
F2 = 3-22
F3 = 28-32
COV = F1*F2*F3'

#using a 2 parameter model with quasi-monte carlo estimation
library(mirt)
les_out = mirt(data.frame(dat), leslie, "2PL", method = 'QMCEM')

#model results
  ##note: IRTpars = TRUE gives 'b' parameter instead of 'd' parameter
coef(les_out, simplify = TRUE, IRTpars = TRUE)

#fit indicies
M2(les_out, QMC = TRUE, na.rm = TRUE)

```
  
  
# The Richard et al. Model  
This model proposes two strategies:  
+ **Minority opportunity-based DEM practices**, which includes internships for racial minorities, mentoring, network groups, and career tracks  
+ **Manager accountability DEM practices**, which includes performance appraisal and bonuses tied to diversity goals  

```{r}
## one option for the richard model; retaining other option as it had better fit

#F1 = minority DEM practices, F2 = manager accountability practices
  ##note: version 1 of the Richard model 
rich1 = 'F1 = 33-36
F2 = 3-6 
COV = F1*F2'

#using a 2 parameter model with quasi-monte carlo estimation
rich1_out = mirt(data.frame(dat), rich1, "2PL", method = 'QMCEM')

#model results
coef(rich1_out, simplify = TRUE, IRTpars = TRUE)

#fit indicies
M2(rich1_out, QMC = TRUE, na.rm = TRUE)

```
  

## The 5-strategy solution  
Our model proposes 5 strategies:
+ **Diversity Metrics**, which represents practices that evaluate organizational diversity goals  
+ **Goals for Diversity**, which represents the organization's goals for diversity  
+ **Institutionalizing Diversity**, which represents how the organization creates internal practices to sustain progress towards diversity goals  
+ **Talent Acquisition**, which represents recruitment and selection practices to attract and hire diverse talent  
+ **Performance Management**, which represents practices that support existing diverse talent  
```{r}
#F1 = diversity metrics, F2 = goals, F3 = institutionalization, F4 = talent acquisition, F5 = performance management
five_s = 'F1 = 14-20
F2 = 7-13
F3 = 1-4, 21-22
F4 = 23-30
F5 = 5-6, 31-36
COV = F1*F2*F3*F4*F5'

#using a 2 parameter model with quasi-monte carlo estimation
five_out = mirt(data.frame(dat), five_s, "2PL", method = 'QMCEM')

#model results
coef(five_out, simplify = TRUE, IRTpars = TRUE)

#fit indicies
M2(five_out, QMC = TRUE, na.rm = TRUE)


```





